---
title: "Homework 1"
author: Sherry Yan
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```

##Problem 1

Create a data frame from the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm( 10 ),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"), 
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```


Take the mean of each variable in my data frame.

```{r}
mean (pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))

```

```{r}
as.numeric (pull(prob1_df, samp))
as.numeric (pull(prob1_df, samp_gt_0))
as.numeric (pull(prob1_df, char_vec))
as.numeric (pull(prob1_df, factor_vec))

```


```{r}
as.numeric (pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp_gt_0)
```

```{r}
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp_gt_0)
```

```{r}
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp_gt_0)
```


Logical variables can be converted to numeric values but character and factors cannot, so I can take the mean of numbers and logical variables but not character or factors.
Converting logical vector to a factor is not meaningful but we can still do it. 
##Problem 2

#install the penguins dataset.

```{r install}
install.packages("palmerpenguins")
```

#load the penguins dataset.

```{r load}
data("penguins", package = "palmerpenguins")
```

#Description of the penguins dataset using inline R code
```{r description}
library(palmerpenguins)
data("penguins")
head(penguins)

`?penguins` gives me information about values of each variable :
  This dataset includes measurements for penguin species, island in Palmer Archipelago, size (flipper length, body mass, bill dimensions), and sex. This is a subset of penguins_raw.

This dataset has 344 rows(observations) and 8 variables(columns), which includes:

species
a factor denoting penguin species (Adélie, Chinstrap and Gentoo)

island
a factor denoting island in Palmer Archipelago, Antarctica (Biscoe, Dream or Torgersen)

bill_length_mm
a number denoting bill length (millimeters)

bill_depth_mm
a number denoting bill depth (millimeters)

flipper_length_mm
an integer denoting flipper length (millimeters)

body_mass_g
an integer denoting body mass (grams)

sex
a factor denoting penguin sex (female, male)

year
an integer denoting the study year (2007, 2008, or 2009)



`variable.names(penguins)` gives me names of variables.
```


```{r rows columns}
nrow(penguins)
ncol(penguins)
The dataset has 344 rows  and 8 columns
```



```{r mean flipper length}
mean(pull(penguins,flipper_length_mm),na.rm=TRUE)
The mean of flipper length is 200.9152 mm.
```


```{r scatterplot}


ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point()

ggsave("P8105_hw1_Q2_scatter_plot.pdf")


```

